Wasted Money? Changes in Toronto's Annual Police Budget and Reported

### 2024-09-27 paper/paper.qmd
Updated header

---
title: "Wasted Money? Changes in Toronto's Annual Police Budget and Reported
Crimes From 2020 to 2023"
author: 
  - Yisu Hou
thanks: "Code and data supporting this analysis are available at: 
https://github.com/YisuHou1/Toronto-Police-Budget-Statistics."
date: today
date-format: long
abstract: "This study analyzed Toronto's annual police budget and crime statistics from 2020 to 2023 using R to assess the budget's effectiveness in preventing crime. Results showed that reported crimes steadily increased while the clearance rate declined over time. Budget changes, including increases from 2020 to 2022 and a reduction from 2022 to 2023, had no significant impact on crime rates. The lack of a relationship between the police budget and crime suggests that Toronto's current crime prevention strategies may be ineffective and that the police budget could be misallocated. These findings highlight the need to reevaluate strategies for ensuring the safety of Toronto's citizens."
format: pdf
header-includes:
  - \usepackage{indentfirst}
  - \setlength{\parindent}{2em}
  - \setlength{\parskip}{0.5em}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{placeins}
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Wasted Money? Changes in Toronto's Annual Police Budget and Reported
Crimes From 2020 to 2023"
author: 
  - Yisu Hou
thanks: "Code and data supporting this analysis are available at: 
https://github.com/YisuHou1/Toronto-Police-Budget-Statistics."
date: today
date-format: long
abstract: "This study analyzed Toronto's annual police budget and crime statistics from 2020 to 2023 using R to assess the budget's effectiveness in preventing crime. Results showed that reported crimes steadily increased while the clearance rate declined over time. Budget changes, including increases from 2020 to 2022 and a reduction from 2022 to 2023, had no significant impact on crime rates. The lack of a relationship between the police budget and crime suggests that Toronto's current crime prevention strategies may be ineffective and that the police budget could be misallocated. These findings highlight the need to reevaluate strategies for ensuring the safety of Toronto's citizens."
format: pdf
header-includes:
  - \usepackage{indentfirst}
  - \setlength{\parindent}{2em}
  - \setlength{\parskip}{0.5em}
  - \usepackage{float}
  - \usepackage{placeins}
number-sections: true
bibliography: references.bib
---
